---
title: "EDA Investment Online"
author: "Meagan Gentry"
date: "April 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
# Basic libraries
library(tidyverse)
library(readxl)
library(fpp2)
library(changepoint)
library(readxl)
```

## Exploratory data analysis of APEM Investment data:

Lingering issues include

* Currency for each country are unidentified, as well as scale
* SEM program and Public route (only) have investment numbers available
* Hong Kong, Singapore, and Korea (only) have investmnet numbers available
* Unsure if week start is referring to fiscal year or calendar year

```{r}
# EDA for media spend APEM Investment data
apem <- read_excel("data/APEM Investment data.xlsx")
apem$`Week Start` = as.Date(apem$`Week Start`)

# Get a view of the data
#summary(apem)
#glimpse(apem)
```

```{r}
# By Country, Route, program, and 'Week Start',
# get totals for net and gross investment
  
apem_net_ <- apem %>% spread(Country, Net_actual_investment, fill=0, sep='_') %>% select(-Gross_actual_investment) 

apem_gross_ <- apem %>% spread(Country, Gross_actual_investment, fill=0, sep='_' )%>% select(-Net_actual_investment)

apem_country <- apem %>% group_by(Country, `Week Start`) %>% 
  summarise(Net_actual_investment = sum(Net_actual_investment),
            Gross_actual_investment = sum(Gross_actual_investment))
```

```{r}
min <- as.Date("2016-07-04")
max <- as.Date("2018-04-16")
```

## APEM Investment by Country
```{r, echo=FALSE}
p <- ggplot(apem_country, aes(x = `Week Start`, y = Net_actual_investment)) + 
  geom_line(aes(color = Country), size = 1) +
 # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_date(limits = c(min, max)) +
  theme_minimal() 

p 
```

### Honk Kong SEM Public 
```{r, echo=FALSE}
apem_hk <- apem_country %>% filter(Country=='Hong Kong')

p <- ggplot(apem_hk, aes(x = `Week Start`, y = Net_actual_investment)) + 
  geom_line(aes(color = Country), size = 1) +
  # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_date(limits = c(min, max)) +
  theme_minimal() 

p

p + stat_smooth(
  color = "#FC4E07", fill = "#FC4E07",
  method = "loess"
)
```

### Singapore SEM Public
```{r, echo=FALSE}
apem_sg <- apem_country %>% filter(Country=='Singapore')

p <- ggplot(apem_sg, aes(x = `Week Start`, y = Net_actual_investment)) + 
  geom_line(aes(color = Country), size = 1) +
  # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_date(limits = c(min, max)) +
  theme_minimal() 

p

p + stat_smooth(
  color = "#FC4E07", fill = "#FC4E07",
  method = "loess"
)
```

### Korea SEM Public
```{r, echo=FALSE}
apem_kr <- apem_country %>% filter(Country=='Korea')

p <- ggplot(apem_kr, aes(x = `Week Start`, y = Net_actual_investment)) + 
  geom_line(aes(color = Country), size = 1) +
  # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_date(limits = c(min, max)) +
  theme_minimal() 

p

p + stat_smooth(
  color = "#FC4E07", fill = "#FC4E07",
  method = "loess"
)
```


## Exploratory data analysis of JP Investment data:
```{r}
# EDA for media spend JP Investment data

read_excel_allsheets <- function(filename, tibble = FALSE) {
  sheets <- readxl::excel_sheets(filename)
  x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
  if(!tibble) x <- lapply(x, as.data.frame)
  names(x) <- sheets
  x
}

jp_sheets <- read_excel_allsheets("data/jp_dg_spend.xlsx")

jp_sheets <- lapply(jp_sheets, function(X) X[,c(4,6)])

jp <- do.call('rbind', jp_sheets)

jp$program <- rep(names(jp_sheets), each = 111)
jp$`Week Start Date` <- as.Date(jp$`Week Start Date`)
```

```{r}
min <- as.Date("2016-04-01")
max <- as.Date("2018-03-26")
```

## Japan Investment Data (All channels)

Lingering issues include

* Currency is unknown, as well as scale
* Unsure how the programs (Lenovo vs NEC) should map to attribution data

## Japan Investment by program (most are obscured)
```{r, echo=FALSE}
p <- ggplot(jp, aes(x = `Week Start Date`, y = Spend)) + 
  geom_line(aes(color = program), size = 1) +
  # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_date(limits = c(min, max)) +
  theme_minimal() 

p
```

### Each JP program and a smoothed trend:
```{r, echo=FALSE}
jp_plots = list()
for (i in unique(jp$program)) {
  jp_ <- jp %>% filter(program == i)
  
  p <- ggplot(jp_, aes(x = `Week Start Date`, y = Spend)) + 
    geom_line(aes(color = program), size = 1) +
    # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
    scale_x_date(limits = c(min, max)) +
    theme_minimal() 
  
  print(
    p +
      stat_smooth(
            color = "#FC4E07", fill = "#FC4E07",
            method = "loess"
      )
  )
}
```

## US Investment Data (SEM only)

```{r}
usca_sem <- read_excel('data/us_ca_sem_spend.xlsx')

usca_sem$`Week Start` <- as.Date(usca_sem$`Week Start`)
```


```{r, echo=FALSE}
p <- ggplot(usca_sem, aes(x = `Week Start`, y = `Total Cost`)) + 
  geom_line(aes(color = program), size = 1) +
  # scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_x_date(limits = c(min, max)) +
  theme_minimal() 

p +
      stat_smooth(
            color = "#FC4E07", fill = "#FC4E07",
            method = "loess"
      )
```

